---
title: "index"
author: "Jorge VM"
date: "2025-02-28"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(languageR)
library(untidydata)
```


```{r}
data(package = "languageR") 
data(package = "untidydata")

```

```{r}
lg_div <- language_diversity |>
  pivot_wider(
    names_from = "Measurement",
    values_from = "Value"
  )
  
```

#descriptive statistics
```{r}
lg_div|>
  group_by(Continent)|>
  summarise(
    langmean = mean(Langs),
    aremean = mean(Area)
  )

```

#model
```{r}
model1 <- lm(
  Langs ~ Area,
  data = lg_div
)
print(model1)
```

#linear model
```{r}
lg_div|>
  ggplot() +
  aes(x = Langs , y = Area) +  
  labs(x = "Languages", y = "Area", title = "Number of languages by area") + 
  geom_point() +
  geom_smooth(method = "lm")

```

#The scatter plot suggests that there is a correlation between an area size and number of languages spoken. The area size includes information about a country size and the number of languages spoken in that territory. The correlation between these two variables is sound, as it is expected that in general, a bigger territory will have more population and within it, more language diversity.    









